The limits of self commitment and private paternalism \thanks{}

### 2021-11-13 choice_benefit.tex
Learning by not doing regressions

\begin{figure}[H]
    \caption{}
    \label{}
    \begin{center}
    %\begin{subfigure}{0.4\textwidth}
    %    \caption{Financial cost}
    %    \centering
    %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
    %\end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Effective cost/loan benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_choice.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Repayment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_choice_des.pdf}
    \end{subfigure}

@@

@@

\begin{figure}[H]
    \caption{Probability of being Type 1 vs HTE}
    \label{}
    \begin{center}
    \begin{subfigure}{0.475\textwidth}
        \caption{Prior Probability}
        \centering
        \includegraphics[width=\textwidth]{Figuras/binscatter_tau_classpr.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Posterior Probability}
        \centering
        \includegraphics[width=\textwidth]{Figuras/binscatter_tau_classpost.pdf}
    \end{subfigure}

@@

\begin{figure}[H]
    \caption{Type 1 class vs HTE}
    \label{}
    \begin{center}
    \begin{subfigure}{0.475\textwidth}
        \caption{Prior Probability}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_type1.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Posterior Probability}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_type1p.pdf}
    \end{subfigure}

@@

\begin{table}[H]
\caption{Outcome in 2S : Choose FP contract}
\label{iv_pf}
\begin{center}
\scriptsize{\input{./Tables/iv_reg_demand_pf_notchoosing.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{iv\_reg\_demand\_pf\_notchoosing.do}
\end{table}

@@

\begin{table}[H]
\caption{Outcome in 2S : Default}
\label{iv_def}
\begin{center}
\scriptsize{\input{./Tables/iv_reg_def_notchoosing.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{iv\_reg\_demand\_pf\_notchoosing.do}
\end{table}

\begin{table}[H]
\caption{Outcome in 2S : Default}
\label{iv_def_decomp}
\begin{center}
\scriptsize{\input{./Tables/iv_reg_def_nc_nr.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{iv\_reg\_demand\_pf\_notchoosing.do}
\end{table}

@@

@@

\begin{figure}[H]
     \caption{TOT-TUT CDF}
    \label{ExplanatoryMaterial}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_tot_tut.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize
        ECDF of the conditional (heterogeneous) TOT \& TUT, alogn with the difference and a test for the difference in means (which is significant).
          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut\_insforest.do}}
\end{figure}

>>>>

\begin{figure}[H]
    \caption{}
    \label{}
    \begin{center}
    %\begin{subfigure}{0.4\textwidth}
    %    \caption{Financial cost}
    %    \centering
    %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
    %\end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Effective cost/loan benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_eff.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Repayment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_des.pdf}
    \end{subfigure}

@@

Based of the propensity score, we predict the two categories : choosers \& non-choosers, such that the proportions match the observed data.

\begin{figure}[H]
    \caption{}
    \label{}
    \begin{center}
    %\begin{subfigure}{0.4\textwidth}
    %    \caption{Financial cost}
    %    \centering
    %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
    %\end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Effective cost/loan benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_eff.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Repayment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_des.pdf}
    \end{subfigure}

    \end{center}
     \scriptsize    CDF of the heterogeneous treatment effect for choosers vs non-choosers. The dotted line below indicates the points where the difference in the distributions is significant.  Instead of a single global null hypothesis (that the two CDFs are identical), there is a continuum of individual null hypotheses of CDF equality at each point. The methodology was proposed by \cite{GOLDMAN2018143}.

          %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
\end{figure}

We find a surprising \emh{significant} stochastic dominance between the two CDF's.

@@

\begin{figure}[H]
    \caption{Probability of being Type 1 vs HTE}
    \label{}
    \begin{center}
    \begin{subfigure}{0.7\textwidth}
        \caption{Posterior Probability}
        \centering
        \includegraphics[width=\textwidth]{Figuras/binscatter_tau_classpost.pdf}
    \end{subfigure}

@@

\begin{figure}[H]
    \caption{Type 1 class vs HTE}
    \label{}
    \begin{center}
    \begin{subfigure}{0.7\textwidth}
        \caption{Posterior Probability}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_type1p.pdf}
    \end{subfigure}

@@

\begin{table}[H]
\caption{Outcome in 2S : Choose FP contract}
\label{iv_pf}
\begin{center}
\scriptsize{\input{./Tables/iv_reg_pago_fijo_detailed.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{iv\_reg\_detailed.do}
\end{table}

@@

We drop murky cases:

\begin{table}[H]
\caption{Keeping only first two observations}
\begin{center}
\scriptsize{\input{./Tables/iv_reg_pago_fijo_detailed_twoca.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{iv\_reg\_detailed.do}
\end{table}

\begin{table}[H]
\caption{Collapsing observations}
\begin{center}
\scriptsize{\input{./Tables/iv_reg_pago_fijo_detailed_colla.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{iv\_reg\_detailed.do}
\end{table}

\begin{table}[H]
\caption{Interacting with number of decision epochs}
\begin{center}
\scriptsize{\input{./Tables/iv_reg_pago_fijo_detailed_inter.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{iv\_reg\_detailed.do}
\end{table}
Learning is stronger after some experience.\\

What about the impact of the previous outcome (default) on learning?

We estimate the following specification:

\begin{align*}
    \mathbbm{1}(\text{Has FP})_{ijt} &= \alpha_i + \gamma_t + \beta_1\mathbbm{1}(\text{Had FP})_{ijt} \\
    & \qquad \quad + \beta_2\mathbbm{1}(\text{Defaulted})_{ijt} \\
    & \qquad \quad  + \beta_3\mathbbm{1}(\text{Had FP})_{ijt}\mathbbm{1}(\text{Defaulted})_{ijt}   + \epsilon_{ijt}
\end{align*}

\begin{table}[H]
\caption{Interaction with default in the past}
\begin{center}
\scriptsize{\input{./Tables/iv_reg_pago_fijo_def_detailed.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{iv\_reg\_intdef\_detailed.do}
\end{table}

And as before we can also get rid of the `murky' cases:

% \begin{table}[H]
% \caption{Keeping only first two observations}
% \begin{center}
% \scriptsize{\input{./Tables/iv_reg_pago_fijo_def_twocases.tex}}
% \end{center}
%  \scriptsize

% %\textit{Do file: } \texttt{iv\_reg\_intdef\_detailed.do}
% \end{table}

\begin{table}[H]
\caption{Collapsing}
\begin{center}
\scriptsize{\input{./Tables/iv_reg_pago_fijo_def_collapsed.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{iv\_reg\_intdef\_detailed.do}
\end{table}

\subsection{Learning in the experiment}

\begin{table}[H]
\caption{Summary statistics table of learning by not doing (OLS)}
\begin{center}
\scriptsize{\input{./Tables/SS_learning_OLS.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{learning\_exp.do}
\end{table}

The above means can be recovered from the following specification

\begin{align*}
    \text{Choose Fee}_{i} &=  \alpha +  \beta_1\mathds{1}(\text{Default past})_{i} +\sum_{j=1}^{4}\beta_{2,j}\mathds{1}(\text{Past contract}=j)_{i} \\
   &\qquad\quad  +\sum_{j=1}^{4}\beta_{3,j}\mathds{1}(\text{Past contract}=j)_{i}\mathds{1}(\text{Default past})_{i} + \epsilon_i
\end{align*}
for those individuals $i$ that had the option to choose after experiencing contract $j$, this could be control, forced fee, or choice.

So what if we add fixed effects to the above? In order to capture variation within individuals in line with our previous specifications in the observational study.

\begin{table}[H]
\caption{Summary statistics table of learning by not doing (FE)}
\begin{center}
\scriptsize{\input{./Tables/SS_learning_FE.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{learning\_exp.do}
\end{table}

\begin{table}[H]
\caption{Learning by not doing (experimental)}
\begin{center}
\scriptsize{\input{./Tables/learning_exp.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{learning\_exp.do}
\end{table}

@@

\begin{figure}[H]
    \caption{Bootstrap inference for the difference between TOT-TUT}
    \label{}
    \begin{center}
    \begin{subfigure}{0.475\textwidth}
        \caption{Simple}
        \centering
        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp1.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Admin controls}
        \centering
        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp2.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Survey controls}
        \centering
        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp3.pdf}
    \end{subfigure}

    \end{center}
     \scriptsize    Binscatter of propensity to choose commitment vs treatment effect of frequent payments.
          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut.do}}
\end{figure}

@@

\begin{figure}[H]
     \caption{TOT-TUT CDF}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_tot_tut.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize
        ECDF of the conditional (heterogeneous) TOT \& TUT, alogn with the difference and a test for the difference in means (which is significant).
          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut\_insforest.do}}
\end{figure}

We test the exclusion restriction

\begin{figure}[H]
     \caption{Exclusion restriction}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/exclusion_restriction.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize

          %\footnotesize{ \textit{Do file: }  \texttt{exclusion\_restriction.do}}
\end{figure}

### 2021-11-13 choice_benefit_summary.tex
Learning by not doing regressions

We investigate the relation between choice (commitment) and benefit. First, we compute the Treatment Effect benefit in the control vs fee arm. Then, we calculate a propensity to choose commitment, and analyze the correlation between this two variables.

\begin{figure}[H]
    \caption{}
    \label{}
    \begin{center}
    %\begin{subfigure}{0.4\textwidth}
    %    \caption{Financial cost}
    %    \centering
    %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
    %\end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Effective cost/loan benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_eff.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Repayment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_des.pdf}
    \end{subfigure}

    \end{center}
     \scriptsize    Binscatter of propensity to choose commitment vs treatment effect of frequent payments.
          %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
\end{figure}

@@

\begin{figure}[H]
    \caption{}
    \label{}
    \begin{center}
    %\begin{subfigure}{0.4\textwidth}
    %    \caption{Financial cost}
    %    \centering
    %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
    %\end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Determinants of HTE}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_eff_cost_loan_pro_2.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Determinants of PS}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/ps_int_vertical_pr_gbc_1.pdf}
    \end{subfigure}

    \end{center}
     \scriptsize  (a): This figure estimates bivariate regressions of the estimated client-level heterogeneous treatment effects against the respective covariate from the baseline survey  $\widehat{hte_i} = \alpha + \beta \: X_i + \epsilon_i$. The regressors $X_i$ include (e.g if the family asks for money, if they have savings, if they are overconfident using the definition the text, etc. See this Appendix for a transcription of the survey). \\
     (b) :  
      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}} \texttt{benefit\_choice.do}}
\end{figure}

\subsection{Are the people who benefit most from commitment, the ones who demand it?}

We estimate the following model

We would like to make a distinction of the people that benefit most from being forced. Our conjecture is that this are the naive individuals.

We assume the following structural model.

Each individual $i$ is of type  $k\in\{1, 2\}$ with probability $\alpha_{i,k}$. We assume it follows a logit distribution:
\begin{align*}
\label{dist_alpha}
    \alpha_{i,k} = \Pr(\text{Type}_i = k \;|\; \mathbf{W}_{i}) = \frac{e^{\gamma_{k}\mathbf{W}_i}}{\sum_{j=1}^{K} e^{\gamma_{j}\mathbf{W}_i}}
\end{align*}

where $\mathbf{W}_i$ are observable characteristics. This characteristics include choice for commitment, present bias, subjective probability of recovery, etc, which might be indicators of naivete vs sophistication.

Now, given their type, each individual makes a choice to default or not $c_{i,k} \in \{1,2\}$, based on other set of observable characteristics $\mathbf{X}_i$ (subjective \& objective value of the loan). We will assume there is a continuous latent variable $Y_{i,k,c}$ distributed as
\[Y_{i,k,c} = \beta_{c,k}\mathbf{X}_{i} +\epsilon_{c,k}\]
with\footnote{We can impose other errors, and even impose a covariance structure, for instance if $(\epsilon_{c,k})_{c}\sim\mathcal{N}(0,\Sigma_k)$, we arrive to the Multinomial Probit.} $\epsilon_{c;k}\sim\operatorname{EV}(0,1)$. This latent variable can be thought of as the utility associated with individual $i$, being type $k$, making choice $c$.

Thus, the density for each individual $i$ being type $k$ is
\[f(c_i,\mathbf{X}_i; \bm\beta_{k}) = \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=4]}\]

Finally, the generative model is then a mixture model with density given by,
\begin{align*}
    f(c_i ,\mathbf{W}_i, \mathbf{X}_i; \bm{\gamma},\bm{\beta}) &= \sum_{k=1}^K \alpha_k f(c_i,\mathbf{X}_i; \bm\beta_{k}) \\
    &= \sum_{k=1}^K \alpha_k \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=c]} 
\end{align*}

where $\alpha\sim \operatorname{Categorical}$, and $\gamma_{K} = \beta_{4,k}=0$ for identification purposes.

Then the (incomplete) log-likelihood function is
\begin{align*}
    \ell(\bm{\gamma}, \bm{\beta}; c, \mathbf{W},  \mathbf{X}) = \sum_{i=1}^n \log\sum_{k=1}^K \alpha_k \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=c]} 
\end{align*}

, thus we estimate parameters $(\bm{\gamma}, \bm{\beta})$ with an EM algorithm using choice (default)
\& observable characteristics: $(c_i,\mathbf{W}_i,\mathbf{X}_i)$.

The results are the following:

\begin{table}[H]
\caption{FMM}
\label{iv_pf}
\begin{center}
\scriptsize{\input{./Tables/fmm_types.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{fmm.do}
\end{table}

The class (type) which is positively correlated with demand for commitment might be identified with the \emph{sophisticated} individuals (Type 2). The hypothesis is that this class is the less benefit from being forced, and so (Type 1) individuals are the most benefited from being forced.

\begin{figure}[H]
    \caption{Probability of being Type 1 vs HTE}
    \label{}
    \begin{center}
    \begin{subfigure}{0.7\textwidth}
        \caption{Posterior Probability}
        \centering
        \includegraphics[width=\textwidth]{Figuras/binscatter_tau_classpost.pdf}
    \end{subfigure}

    \end{center}
     \scriptsize 
      %\footnotesize{ \textit{Do file: }  \texttt{fmm.do}} 
\end{figure}

A negative relation indicates that being Type 1 has more benefits from being forced.

\begin{figure}[H]
    \caption{Type 1 class vs HTE}
    \label{}
    \begin{center}
    \begin{subfigure}{0.7\textwidth}
        \caption{Posterior Probability}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_type1p.pdf}
    \end{subfigure}

    \end{center}
     \scriptsize 
      %\footnotesize{ \textit{Do file: }  \texttt{fmm.do}} 
\end{figure}

Moreover we find a strong correlation between the Type 1 individuals and the individuals that ``choose wrong" according to Figure 8 \ref{choose_wrong}.\\

\emph{This exercise is stronger in the sense that when we divide by type, choice is the core divider.} This emphasizes how important choice is as a segregator.

\subsection{Observational Study}

Paternalism  with learning : We generate more learning through forcing than through choice.

It is possible that the wrong people choose and they learn not through choosing, but rather through not choosing (and it did not work). We then partition our sample in the observational study, based on whether you committed the first time, and we want to show that learning happened in the "wrong group" : not choosers.

We want to show that the TE is localized within one of the groups in that endogenous split.

We then estimate the following two-stage specification.

@@

We drop murky cases:

@@

@@

%\textit{Do file: } \texttt{iv\_reg\_detailed.do}
\end{table}
Learning is stronger after some experience.\\

What about the impact of the previous outcome (default) on learning?

We estimate the following specification:

@@

\subsection{Learning in the experiment}

@@

@@

@@

@@

\begin{figure}[H]
    \caption{Bootstrap inference for the difference between TOT-TUT}
    \label{}
    \begin{center}
    \begin{subfigure}{0.475\textwidth}
        \caption{Simple}
        \centering
        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp1.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Admin controls}
        \centering
        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp2.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Survey controls}
        \centering
        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp3.pdf}
    \end{subfigure}

    \end{center}
     \scriptsize    Binscatter of propensity to choose commitment vs treatment effect of frequent payments.
          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut.do}}
\end{figure}

\begin{figure}[H]
     \caption{TOT-TUT Histogram}
    \label{}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/dif_tot_tut.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize
        Histogram for the difference of the conditional (heterogeneous) TOT-TUT
          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut\_insforest.do}}
\end{figure}

\begin{figure}[H]
     \caption{TOT-TUT CDF}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_tot_tut.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize
        ECDF of the conditional (heterogeneous) TOT \& TUT, alogn with the difference and a test for the difference in means (which is significant).
          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut\_insforest.do}}
\end{figure}

@@

\begin{figure}[H]
     \caption{Exclusion restriction}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/exclusion_restriction.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize

@@

\newpage
\section{Appendix : Mixture Model}
Mixing distributions and mixture models are able to approximate the density function of any unknown distribution to arbitrary degrees of accuracy, provided that the mixing or mixture distribution  is  sufficiently  complex \cite{nguyen}. In fact, \cite{mcfadden} demonstrated that any random utility model can be approximated to any degree of accuracy by a mixed logit with the appropriate specification of variables and mixing distribution. We follow the approach by \cite{TRAIN200840}.\\

\subsection{Estimation}

The EM algorithm following \cite{em,em_seq} but most importantly \cite{TRAIN200840}, is in our setting :

\begin{algorithm}[H]
\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}

\caption{EM}\label{EM}
\small{
\Input{$(c_i, \mathbf{W}_i,  \mathbf{X}_i)$}
\Output{$\hat{\bm\gamma}, \hat{\bm{\beta}}, \widetilde{\alpha_{i,k}}, \widetilde{\alpha_{k}}$}
\BlankLine
Initialize $\gamma_{k}^{(0)}, \beta_k^{(0)}$

Update the predicted probability (weight) for individual $i$, type $k$: \;
$\widehat{\alpha_{i,k}^{(0)}} = \frac{e^{\gamma_{k}^{(0)}\mathbf{W}_i}}{\sum_{j=1}^{K} e^{\gamma_{j}^{(0)}\mathbf{W}_i}} $
% $\alpha_{i}^{(0)}\sim \operatorname{Categorical}$, following (\ref{dist_alpha})

Update the shares of types:\;
$\widehat{\alpha_k^{(0)}} = \frac{\sum_{i=1}^n\widehat{\alpha_{i,k}^{(0)}}}{\sum_{k=1}^{K}\sum_{i=1}^n\widehat{\alpha_{i,k}^{(0)}}}$\;

\textbf{E-step :}

Compute predicted posterior probability  for the $k$ type: \;
$\widetilde{\alpha_{i,k}^{(0)}} = \frac{\widehat{\alpha_k^{(0)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(0)})}{\sum_{k=1}^K\widehat{\alpha_k^{(0)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(0)})}$\;

\While{$||(\bm\gamma^{(t)},\bm\beta^{(t)})-(\bm\gamma^{(t-1)},\bm\beta^{(t-1)})||>\operatorname{tol}$}{

\textbf{M-step :}

$\bm\beta_{k}^{(t+1)}  = \operatorname{argmax}_{\bm\beta_{k}} \sum_{i=1}^n \widetilde{\alpha_{i,k}^{(t)}} \log \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=c]} $\;
\scriptsize{(Run a multinomial-logit model with weighted observations, with weights given by the conditional probabilities of type membership)}\;
\small

$\bm\gamma_{k}^{(t+1)} = \operatorname{argmax}_{\bm\gamma_{k}} \sum_{i=1}^n\sum_{k=1}^K \widetilde{\alpha_{i,k}^{(t)}} \log \left(\frac{e^{\gamma_{k}\mathbf{W}_i}}{\sum_{j=1}^{K} e^{\gamma_{j}\mathbf{W}_i}}\right) $\;

\scriptsize{(Grouped-data log likelihood, where we have used a multinomial-logit specification)}\;

\small

Update the predicted probability (weight) for individual $i$, type $k$: \;
$\widehat{\alpha_{i,k}^{(t+1)}} = \frac{e^{\gamma_{k}^{(t+1)}\mathbf{W}_i}}{\sum_{j=1}^{K} e^{\gamma_{j}^{(t+1)}\mathbf{W}_i}} $
% $\alpha_{i}^{(0)}\sim \operatorname{Categorical}$, following (\ref{dist_alpha})

Update the shares of types:\;
$\widehat{\alpha_k^{(t+1)}} = \frac{\sum_{i=1}^n\widehat{\alpha_{i,k}^{(t+1)}}}{\sum_{k=1}^{K}\sum_{i=1}^n\widehat{\alpha_{i,k}^{(t+1)}}}$\;

\textbf{E-step :}

Compute predicted posterior probability  for the $k$ type: \;
$\widetilde{\alpha_{i,k}^{(t+1)}} = \frac{\widehat{\alpha_k^{(t+1)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(t+1)})}{\sum_{k=1}^K\widehat{\alpha_k^{(t+1)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(t+1)})}$\;

}
Update the posterior shares of types:\;
$\widetilde{\alpha_k^{(t+1)}} = \frac{\sum_{i=1}^n\widetilde{\alpha_{i,k}^{(t+1)}}}{\sum_{k=1}^{K}\sum_{i=1}^n\widetilde{\alpha_{i,k}^{(t+1)}}}$\;
}
\end{algorithm}

\subsection{Extensions}

A stochastic version\footnote{See \cite{nielsen}.} of the estimation above consists, at iteration $t$, in replacing the probability of the unknown types $k$ by a sequence sampled from a Categorical distribution
\[\widehat{\alpha_{i}^{(t)}}\sim \operatorname{Categorical}\left(\frac{\widehat{\alpha_k^{(t+1)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(t+1)})}{\sum_{k=1}^K\widehat{\alpha_k^{(t+1)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(t+1)})}\right)\] 
We call this the \textbf{SE-step}. We can then use these sampled labels for updating the estimation in the \textbf{M-step} by maximizing the \emph{complete} maximum likelihood.

\subsubsection{Degrees of naivete}
We can model degrees of naivete assuming every individual $i$ has a (continuous) propensity of being of each type. We model this by making the predicted probability of each individual follow a Dirichlet regression $\alpha_{i} \sim \operatorname{DirichletReg}$.

\subsection{Identifiability}
\cite{grun} analyze the identifiability of a general class of finite mixtures of multinomial logits.

>>>>

@@

\newpage

\section{Observational Study}

\subsection*{Paternalism  with learning : We generate more learning through forcing than through choice.}

It is possible that the wrong people choose and they learn not through choosing, but rather through not choosing (and it did not work). We then partition our sample in the observational study, based on whether you committed the first time, and we want to show that learning happened in the ``wrong group" : not choosers.\\

We want to show that the TE is localized within one of the groups in that endogenous split. With that in mind, we estimate the following two-stage specification.

@@

\newpage

\subsection*{The results are robust when dropping `` murky" cases:}

@@

\subsection*{Learning is stronger after some experience.}

@@

\subsection*{What about the impact of the previous outcome (default) on learning?}

We estimate the following specification, instrumenting the previous contract with the availability of the product as before.

@@

\section{Learning with experimantal data}

@@

This might look discouraging, but what if we exploit individual variation?

@@

\subsection*{We find there is learning, and also learning by not doing!}

@@

\newpage

@@

\begin{figure}[H]
    \caption{Bootstrap inference for the difference between TOT-TUT}
    \label{}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
        \caption{Simple}
        \centering
        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp1.pdf}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \caption{Admin controls}
        \centering
        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp2.pdf}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \caption{Survey controls}
        \centering
        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp3.pdf}
    \end{subfigure}

    \end{center}
     \scriptsize   
          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut.do}}
\end{figure}

\begin{figure}[H]
     \caption{TOT-TUT Histogram}
    \label{}
    \begin{center}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/dif_tot_tut.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize
        Histogram for the difference of the conditional (heterogeneous) TOT-TUT
          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut\_insforest.do}}
\end{figure}

\begin{figure}[H]
     \caption{TOT-TUT CDF}
    \begin{center}
    \begin{subfigure}{0.7\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_tot_tut.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize
        ECDF of the conditional (heterogeneous) TOT \& TUT, alogn with the difference and a test for the difference in means (which is significant).
          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut\_insforest.do}}
\end{figure}

@@

\begin{figure}[H]
     \caption{Exclusion restriction}
    \begin{center}
    \begin{subfigure}{0.7\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/exclusion_restriction.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize

@@
